Modalities for Location Virtualization

### 2022-09-20 programlogic.tex
+

To concretize the understanding of these principles achieved with the modal abstraction for address-space, $\modaldef\ell\modalP$, let us first investigate the specification of the instruction ($\textsf{movctl\_instr}$) switching address spaces. Assume that our CPU keeps the current address space based on its page table register CR3, as we see in Figure \fref{fig:addressspaceswitching}
\input{fig-ctlreasoning}

>>>>

To concretize the understanding of these principles achieved with the modal abstraction for address-space, $\modaldef\ell\modalP$, let us first investigate the specification of the instruction ($\textsf{movctl\_instr}$) switching address spaces. Assume that our CPU keeps the current address space based on its page table register CR3, as we see in Figure \fref{fig:addressspaceswitching}.
\input{fig-ctlreasoning}
Thinking of $\modalP$ and $\modalQ$ as resources representing the indirection mappings ($\mapsto_{\kw{p}}$) in the address spaces rooted at $\rvsrc$ and $\rvdst$ respectively, the rule interacts with the ambient logic, \SL, via pulls local state out of the address-space modality rooted at $\rvdst$, and make it the observable view of the memory.
